---
title: "A method for estimating colony size using queen fecundity in termites under field conditions"
output:
  html_document: default
  pdf_document: default
---

```{r}
# All analyses were performed using R v4.2.3.
```

```{r}
# packages
install.packages("readxl")
install.packages("ggplot2")
install.packages("tidyverse")
install.packages("dplyr")
install.packages("lme4")
install.packages("car")

library(readxl)
library(ggplot2)
library(tidyverse)
library(lme4)
library(car)
```

# Mark recapture
```{r}
# data loading and processing
mark <- read_excel("Dataset.xlsx", sheet="mark recapture") %>% 
  mutate(total_W = no_of_unmarked_wrokers + no_of_marked_workers_stayed_in_introduced_log + no_of_marked_workers_dispersed_from_another_log) %>% 
  as.data.frame(.)

mark_r <- mark %>% 
  filter(area == "royal_chamber")
mark_f <- mark %>% 
  filter(area == "foraging")

# marked workers introduced in royal area
introduced_in_royal <- mark_r %>% 
  rename(no_of_marked_workers = no_of_marked_workers_stayed_in_introduced_log) %>% 
  dplyr::select(colony, period_week, no_of_marked_workers, total_W) %>% 
  mutate(category = "stayed")
despersed_to_foraging <- mark_f %>% 
  rename(no_of_marked_workers = no_of_marked_workers_dispersed_from_another_log) %>% 
  dplyr::select(colony, period_week, no_of_marked_workers, total_W) %>% 
  mutate(category = "dispersed")
introduced_in_royal <- rbind(introduced_in_royal, despersed_to_foraging) %>% 
   mutate(origin = "introduced_in_royal")

# marked workers introduced in foraging area
introduced_in_foraging <- mark_f %>% 
  rename(no_of_marked_workers = no_of_marked_workers_stayed_in_introduced_log) %>% 
  dplyr::select(colony, period_week, no_of_marked_workers, total_W) %>% 
  mutate(category = "stayed")
despersed_to_royal <- mark_r %>% 
  rename(no_of_marked_workers = no_of_marked_workers_dispersed_from_another_log) %>% 
  dplyr::select(colony, period_week, no_of_marked_workers, total_W) %>% 
  mutate(category = "dispersed")
introduced_in_foraging <- rbind(introduced_in_foraging, despersed_to_royal) %>% 
   mutate(origin = "introduced_in_foraging")

mark_all <- rbind(introduced_in_royal, introduced_in_foraging)
```

## * sample size
```{r}
summary_mark <- mark %>% 
  group_by(period_week,colony) %>% 
  summarize(mean = mean(no_of_unmarked_wrokers)) %>% 
  summarize(number = n())
summary_mark
```

## * statistical analysis
### * introduced in royal and foraging
#### * effect of test period on distribution of marked workers (all data merged)
```{r}
model_all1 <- glmer(cbind(no_of_marked_workers, total_W-no_of_marked_workers) ~ category * period_week + (1|colony), family = binomial, mark_all)
model_all2 <- glmer(cbind(no_of_marked_workers, total_W-no_of_marked_workers) ~ category + period_week + (1|colony), family = binomial, mark_all)
model_all3 <- glmer(cbind(no_of_marked_workers, total_W-no_of_marked_workers) ~ 1 + period_week + (1|colony), family = binomial, mark_all)

summary(model_all1)
anova(model_all1, model_all2, test="Chi")
```

#### * comparison of distribution of marked workers between areas (all data merged)
```{r}
summary(model_all2)
anova(model_all2, model_all3, test="Chi")
```

### * comparison of distribution of marked workers between areas
#### * 2 weeks
```{r}
model_2w1 <- glmer(cbind(no_of_marked_workers, total_W-no_of_marked_workers) ~ category + (1|colony), family = binomial, mark_all %>% filter(period_week=="2"))
model_2w2 <- glmer(cbind(no_of_marked_workers, total_W-no_of_marked_workers) ~ 1 + (1|colony), family = binomial, mark_all %>% filter(period_week=="2"))
summary(model_2w1)
anova(model_2w1, model_2w2, test="Chi")
```

#### * 4 weeks
```{r}
model_4w1 <- glmer(cbind(no_of_marked_workers, total_W-no_of_marked_workers) ~ category + (1|colony), family = binomial, mark_all %>% filter(period_week=="4"))
model_4w2 <- glmer(cbind(no_of_marked_workers, total_W-no_of_marked_workers) ~ 1 + (1|colony), family = binomial, mark_all %>% filter(period_week=="4"))
summary(model_4w1)
anova(model_4w1, model_4w2, test="Chi")
```


### * introduced in royal
#### * effect of test period on distribution of marked workers
```{r}
model_r1 <- glmer(cbind(no_of_marked_workers, total_W-no_of_marked_workers) ~ category * period_week + (1|colony), family = binomial, introduced_in_royal)
model_r2 <- glmer(cbind(no_of_marked_workers, total_W-no_of_marked_workers) ~ category + period_week + (1|colony), family = binomial, introduced_in_royal)
summary(model_r1)
anova(model_r1, model_r2, test="Chi")
```

#### * comparison of distribution of marked workers between areas in 2 weeks group
```{r}
model_r2_1 <- glmer(cbind(no_of_marked_workers, total_W-no_of_marked_workers) ~ category + (1|colony), family = binomial, introduced_in_royal %>% filter(period_week=="2"))
model_r2_2 <- glmer(cbind(no_of_marked_workers, total_W-no_of_marked_workers) ~ 1 + (1|colony), family = binomial, introduced_in_royal %>% filter(period_week=="2"))
summary(model_r2_1)
anova(model_r2_1, model_r2_2, test="Chi")
```

#### * comparison of distribution of marked workers between areas in 4 weeks group
```{r}
model_r4_1 <- glmer(cbind(no_of_marked_workers, total_W-no_of_marked_workers) ~ category + (1|colony), family = binomial, introduced_in_royal %>% filter(period_week=="4"))
model_r4_2 <- glmer(cbind(no_of_marked_workers, total_W-no_of_marked_workers) ~ 1 + (1|colony), family = binomial, introduced_in_royal %>% filter(period_week=="4"))
summary(model_r4_1)
anova(model_r4_1, model_r4_2, test="Chi")
```

### * introduced in foraging
#### * effect of test period on distribution of marked workers
```{r}
model_f1 <- glmer(cbind(no_of_marked_workers, total_W-no_of_marked_workers) ~ category * period_week + (1|colony), family = binomial, introduced_in_foraging)
model_f2 <- glmer(cbind(no_of_marked_workers, total_W-no_of_marked_workers) ~ category + period_week + (1|colony), family = binomial, introduced_in_foraging)
summary(model_f1)
Anova(model_f1)
anova(model_f1, model_f2, test="Chi")
```

#### * comparison of distribution of marked workers between areas in 2 weeks group
```{r}
model_f2_1 <- glmer(cbind(no_of_marked_workers, total_W-no_of_marked_workers) ~ category + (1|colony), family = binomial, introduced_in_foraging %>% filter(period_week=="2"))
model_f2_2 <- glmer(cbind(no_of_marked_workers, total_W-no_of_marked_workers) ~ 1 + (1|colony), family = binomial, introduced_in_foraging %>% filter(period_week=="2"))
summary(model_f2_1)
anova(model_f2_1, model_f2_2, test="Chi")
```

#### * comparison of distribution of marked workers between areas in 4 weeks group
```{r}
model_f4_1 <- glmer(cbind(no_of_marked_workers, total_W-no_of_marked_workers) ~ category + (1|colony), family = binomial, introduced_in_foraging %>% filter(period_week=="4"))
model_f4_2 <- glmer(cbind(no_of_marked_workers, total_W-no_of_marked_workers) ~ 1 + (1|colony), family = binomial, introduced_in_foraging %>% filter(period_week=="4"))
summary(model_f4_1)
anova(model_f4_1, model_f4_2, test="Chi")
```

## * figure
```{r}
# distribution of marked workers
mark_all$category <- factor(mark_all$category, levels=c("stayed","dispersed")) 

Figure_mark_all <-
ggplot(mark_all,
       aes(y = no_of_marked_workers/total_W,
           x = category,
           ))+
  geom_boxplot() + 
  geom_jitter(#group = "group", 
              color = "black", 
              height = 0, 
              width = 0.2, 
              alpha = 1, 
              size = 1 
              ) +
  facet_wrap(vars(as.factor(period_week)), scales = "free") +
  scale_y_continuous(breaks=seq(0,1,by=0.005),limits=c(0,0.026),expand=c(0,0)) +
  labs(y = "marked worker ratio",
       x = "",
       title ="") +
  theme_classic()
Figure_mark_all

# save figure
ggsave(file = "Figure distribution of marked workers.pdf", plot = Figure_mark_all, dpi = 300, width = 89, height = 89, units = c("mm"))
```


# Variance in body weight of secondary queen
```{r}
# data loading
variance <- read_excel("Dataset.xlsx", sheet="seasonality in queen weight") %>% 
  as.data.frame(.)

variance_c <- variance %>% 
  group_by(colony, month) %>% 
  summarize(mean_body_weight_of_secondary_queen_mg = mean(body_weight_of_secondary_queen_mg)) %>% 
  mutate(mean_body_weight_of_secondary_queen_mg = round(mean_body_weight_of_secondary_queen_mg,2))
```

## * sample size
```{r}
summary_variance <- variance %>% 
  summarize(number = n())
summary_variance

summary_variance_c <- variance_c %>% 
  summarize(number = n())
summary_variance_c
```

## * statistical analysis
```{r}
var.test(mean_body_weight_of_secondary_queen_mg ~ month, variance_c %>% filter(month=="April"|month=="May"))
var.test(mean_body_weight_of_secondary_queen_mg ~ month, variance_c %>% filter(month=="April"|month=="June"))
var.test(mean_body_weight_of_secondary_queen_mg ~ month, variance_c %>% filter(month=="April"|month=="July"))
var.test(mean_body_weight_of_secondary_queen_mg ~ month, variance_c %>% filter(month=="April"|month=="August"))
var.test(mean_body_weight_of_secondary_queen_mg ~ month, variance_c %>% filter(month=="April"|month=="September"))

var.test(mean_body_weight_of_secondary_queen_mg ~ month, variance_c %>% filter(month=="May"|month=="June"))
var.test(mean_body_weight_of_secondary_queen_mg ~ month, variance_c %>% filter(month=="May"|month=="July"))
var.test(mean_body_weight_of_secondary_queen_mg ~ month, variance_c %>% filter(month=="May"|month=="August"))
var.test(mean_body_weight_of_secondary_queen_mg ~ month, variance_c %>% filter(month=="May"|month=="September"))

var.test(mean_body_weight_of_secondary_queen_mg ~ month, variance_c %>% filter(month=="June"|month=="July"))
var.test(mean_body_weight_of_secondary_queen_mg ~ month, variance_c %>% filter(month=="June"|month=="August"))
var.test(mean_body_weight_of_secondary_queen_mg ~ month, variance_c %>% filter(month=="June"|month=="September"))

var.test(mean_body_weight_of_secondary_queen_mg ~ month, variance_c %>% filter(month=="July"|month=="August"))
var.test(mean_body_weight_of_secondary_queen_mg ~ month, variance_c %>% filter(month=="July"|month=="September"))

var.test(mean_body_weight_of_secondary_queen_mg ~ month, variance_c %>% filter(month=="August"|month=="September"))
```

## * figure
```{r}
variance_c$month <- factor(variance_c$month, levels=c("April","May","June","July", "August", "September"))
Fig_SQ_weight <- 
ggplot(variance_c, aes(y = mean_body_weight_of_secondary_queen_mg, x = factor(month))) + 
  geom_boxplot(outlier.shape = NA, 
               width=0.6
               ) + 
  geom_jitter(#group = "group", 
              color = "black", 
              height = 0, 
              width = 0.25, 
              alpha = 0.4, 
              size = 1 
              ) +
  scale_y_continuous(breaks=seq(0,50,by=5),limits=c(0,24),expand=c(0,0)) +
  labs(y = "Mean body weght of secondary queen (mg)", 
       x = "Month",
       title ="") +
  theme_classic()
Fig_SQ_weight

# save figure
ggsave(file = "Figure SQ weight seasonality.pdf", plot = Fig_SQ_weight, dpi = 300, width = 89, height = 89, units = c("mm"))
```


# Correlation between body and ovary weight in secondary queen
```{r}
# loading data
ovary <- read_excel("Dataset.xlsx", sheet="body and ovary weight") %>% 
  as.data.frame(.)
```

## * sample size
```{r}
summary_ovary <- ovary %>% 
  summarize(number = n())
summary_ovary
```

## * statistical analysis
```{r}
model_og <- glm(ovaries_weight_mg ~ log(body_weight_of_secondary_queen_mg), family = Gamma(link = "log"), ovary)
model_og2 <- glm(ovaries_weight_mg ~ 1, family = Gamma(link = "log"), ovary)
summary(model_og)
anova(model_og, model_og2, test="Chi")
Anova(model_og)
```

## * figure
```{r}
Fig_ovary <- 
  ggplot(ovary, aes(y = ovaries_weight_mg, x = body_weight_of_secondary_queen_mg)) +
  stat_function(fun = function(x){exp(coef(model_og)[1] + coef(model_og)[2]*log(x))}) + 
  geom_point(size = 3, shape = 1) +
  labs(x = "SQ body weight (mg)",
       y = "Ovary weight (mg)", 
       title ="") +
  scale_x_continuous(breaks=seq(0,50,by=5),limits=c(0,26)) +
  scale_y_continuous(breaks=seq(0,20,by=5),limits=c(0,16)) +
  theme_classic()
Fig_ovary

# save figure
ggsave(file = "Figure ovary.pdf", plot = Fig_ovary, dpi = 300, width = 89, height = 89, units = c("mm"))
```

## * determinant coefficient (R^2)
```{r}
summary_ymean <- ovary %>% 
  summarize(mean = mean(ovaries_weight_mg))
mean <- summary_ymean$mean[1]

ovary_prep <- ovary %>% 
  mutate(pred = exp(coef(model_og)[1] + coef(model_og)[2]*log(body_weight_of_secondary_queen_mg))) %>% 
  mutate(resid_square = (ovaries_weight_mg - pred)^2) %>% 
  mutate(deviation_square = (ovaries_weight_mg - mean)^2)

ovary_r2 <- ovary_prep %>% 
  summarize(numerator = sum(resid_square),
            denominator = sum(deviation_square)) %>% 
  mutate(r2 = 1 - numerator/denominator)

ovary_r2
```


# Correlation between body weight of secondary queen and egg production
```{r}
# data loading
egg <- read_excel("Dataset.xlsx", sheet="queen weight and egg production") %>% 
  as.data.frame(.)
```

## * sample size
```{r}
summary_egg <- egg %>% 
  group_by(colony) %>% 
  summarize(mean = mean(no_of_eggs_laid)) %>% 
  summarize(number = n())
summary_egg
```

## * statistical analysis
```{r}
model_eg <- glm(no_of_eggs_laid ~ log(body_weight_of_secondary_queen_mg), family = poisson(link = "log"), egg)
model_eg2 <- glm(no_of_eggs_laid ~ 1, family = poisson(link = "log"), egg)
summary(model_eg)
anova(model_eg, model_eg2, test="Chi")
Anova(model_eg)
```

## * figure
```{r}
Fig_egg <- 
  ggplot(egg, aes(y = no_of_eggs_laid, x = body_weight_of_secondary_queen_mg)) +
  stat_function(fun = function(x){exp(coef(model_eg)[1] + coef(model_eg)[2]*log(x))}) +
  geom_point(size = 3, shape = 1) +
  labs(x = "Body weight of queen  (mg)",
       y = "Number of eggs laid (per 24h)", 
       title ="") +
  scale_x_continuous(breaks=seq(-10,50,by=5),limits=c(0,26)) +
  scale_y_continuous(breaks=seq(-40,300,by=20),limits=c(0,130)) +
  theme_classic()
Fig_egg

# save figure
ggsave(file = "Figure egg production.pdf", plot = Fig_egg, dpi = 300, width = 89, height = 89, units = c("mm"))
```

## * determinant coefficient (R^2)
```{r}
summary_ymean <- egg %>% 
  summarize(mean = mean(no_of_eggs_laid))
mean <- summary_ymean$mean[1]

egg_prep <- egg %>% 
  mutate(pred = exp(coef(model_eg)[1] + coef(model_eg)[2]*log(body_weight_of_secondary_queen_mg))) %>% 
  mutate(resid_square = (no_of_eggs_laid - pred)^2) %>% 
  mutate(deviation_square = (no_of_eggs_laid - mean)^2)

egg_r2 <- egg_prep %>% 
  summarize(numerator = sum(resid_square),
            denominator = sum(deviation_square)) %>% 
  mutate(r2 = 1 - numerator/denominator)

egg_r2
```


# Correlation between number of workers and daily egg production
```{r}
# data loading and calculation of number of eggs laid in the colony
egg_estimate <- read_excel("Dataset.xlsx", sheet="colony size and egg production") %>% 
  as.data.frame(.) %>% 
  mutate(daily_egg_production = round((exp(coef(model_eg)[1] + coef(model_eg)[2]*log(mean_body_weight_of_secondary_queen_mg)))*no_of_secondary_queen, 0))
```

## * sample size
```{r}
summary_egg_estimate <- egg_estimate %>% 
  summarize(number = n())
summary_egg_estimate
```

## * statistical analysis
```{r}
model_w_egg <- glm(no_of_worker ~ log(daily_egg_production), family = poisson(link = "log"), egg_estimate)
model_w_egg2 <- glm(no_of_worker ~ 1, family = poisson(link = "log"), egg_estimate)
summary(model_w_egg)
summary(model_w_egg2)
anova(model_w_egg, model_w_egg2, test="Chi")
Anova(model_w_egg)
```

## * figure 
```{r}
Fig_egg_W <- 
  ggplot(egg_estimate, aes(y = no_of_worker, x = daily_egg_production)) +
  stat_function(fun = function(x){exp(coef(model_w_egg)[1] + coef(model_w_egg)[2]*log(x))}) +
  geom_point(size = 3, shape = 1) +
  labs(y = "Number of workers in the colony",
       x = "Total number of eggs laid in the colony (per 24h)", 
       title ="") +
  scale_y_continuous(breaks=seq(0,450000,by=50000),limits=c(0,360000)) +
  scale_x_continuous(breaks=seq(0,6000,by=1000),limits=c(0,4600)) +
  theme_classic()
Fig_egg_W

# save figure
ggsave(file = "Figure W egg.pdf", plot = Fig_egg_W, dpi = 300, width = 89, height = 89, units = c("mm"))
```

## * determinant coefficient (R^2)
```{r}
summary_ymean <- egg_estimate %>% 
  summarize(mean = mean(no_of_worker))
mean <- summary_ymean$mean[1]

egg_estimate_prep <- egg_estimate %>% 
  mutate(pred = exp(coef(model_w_egg)[1] + coef(model_w_egg)[2]*log(daily_egg_production))) %>% 
  mutate(resid_square = (no_of_worker - pred)^2) %>% 
  mutate(deviation_square = (no_of_worker - mean)^2)

egg_estimate_r2 <- egg_estimate_prep %>% 
  summarize(numerator = sum(resid_square),
            denominator = sum(deviation_square)) %>% 
  mutate(r2 = 1 - numerator/denominator)

egg_estimate_r2
```

# Correlation between number of workers and king weight
## * statistical analysis
```{r}
model_w_k <- glm(no_of_worker ~ log(body_weight_of_primary_king_mg), family = poisson(link = "log"), q_estimate)
model_w_k2 <- glm(no_of_worker ~ 1, family = poisson(link = "log"), q_estimate)
summary(model_w_k)
anova(model_w_k, model_w_k2, test="Chi")
Anova(model_w_k)
```

## * determinant coefficient (R^2)
```{r}
summary_ymean <- q_estimate %>% 
  summarize(mean = mean(no_of_worker))
mean <- summary_ymean$mean[1]

q_estimate_prep <- q_estimate %>% 
  mutate(pred = exp(coef(model_w_k)[1] + coef(model_w_k)[2]*log(body_weight_of_primary_king_mg))) %>% 
  mutate(resid_square = (no_of_worker - pred)^2) %>% 
  mutate(deviation_square = (no_of_worker - mean)^2)

q_estimate_r2 <- q_estimate_prep %>% 
  summarize(numerator = sum(resid_square),
            denominator = sum(deviation_square)) %>% 
  mutate(r2 = 1 - numerator/denominator)

q_estimate_r2
```

# Correlation between number of workers and queen mean weight
## * statistical analysis
```{r}
model_w_mq <- glm(no_of_worker ~ log(mean_body_weight_of_secondary_queen_mg), family = poisson(link = "log"), q_estimate)
model_w_mq2 <- glm(no_of_worker ~ 1, family = poisson(link = "log"), q_estimate)
summary(model_w_mq)
anova(model_w_mq, model_w_mq2, test="Chi")
Anova(model_w_mq)
```

## * determinant coefficient (R^2)
```{r}
summary_ymean <- q_estimate %>% 
  summarize(mean = mean(no_of_worker))
mean <- summary_ymean$mean[1]

q_estimate_prep <- q_estimate %>% 
  mutate(pred = exp(coef(model_w_mq)[1] + coef(model_w_mq)[2]*log(mean_body_weight_of_secondary_queen_mg))) %>% 
  mutate(resid_square = (no_of_worker - pred)^2) %>% 
  mutate(deviation_square = (no_of_worker - mean)^2)

q_estimate_r2 <- q_estimate_prep %>% 
  summarize(numerator = sum(resid_square),
            denominator = sum(deviation_square)) %>% 
  mutate(r2 = 1 - numerator/denominator)

q_estimate_r2
```

# Correlation between number of workers and number of queens
## * statistical analysis
```{r}
model_w_nq <- glm(no_of_worker ~ log(no_of_secondary_queen), family = poisson(link = "log"), q_estimate)
model_w_nq2 <- glm(no_of_worker ~ 1, family = poisson(link = "log"), q_estimate)
summary(model_w_nq)
anova(model_w_nq, model_w_nq2, test="Chi")
Anova(model_w_nq)
```

## * determinant coefficient (R^2)
```{r}
summary_ymean <- q_estimate %>% 
  summarize(mean = mean(no_of_worker))
mean <- summary_ymean$mean[1]

q_estimate_prep <- q_estimate %>% 
  mutate(pred = exp(coef(model_w_nq)[1] + coef(model_w_nq)[2]*log(no_of_secondary_queen))) %>% 
  mutate(resid_square = (no_of_worker - pred)^2) %>% 
  mutate(deviation_square = (no_of_worker - mean)^2)

q_estimate_r2 <- q_estimate_prep %>% 
  summarize(numerator = sum(resid_square),
            denominator = sum(deviation_square)) %>% 
  mutate(r2 = 1 - numerator/denominator)

q_estimate_r2
```

# Correlation between number of workers and total queen weight
```{r}
# data loading and calculation of number of eggs laid in the colony
q_estimate <- read_excel("Dataset.xlsx", sheet="colony size and egg production") %>% 
  as.data.frame(.) %>% 
  mutate(daily_egg_production = round((exp(coef(model_eg)[1] + coef(model_eg)[2]*log(mean_body_weight_of_secondary_queen_mg)))*no_of_secondary_queen, 0)) %>% 
  mutate(total_queen_weight = mean_body_weight_of_secondary_queen_mg*no_of_secondary_queen)
```

## * sample size
```{r}
summary_q_estimate <- q_estimate %>% 
  summarize(number = n())
summary_q_estimate
```

## * statistical analysis
```{r}
model_w_q <- glm(no_of_worker ~ log(total_queen_weight), family = poisson(link = "log"), q_estimate)
model_w_q2 <- glm(no_of_worker ~ 1, family = poisson(link = "log"), q_estimate)
summary(model_w_q)
anova(model_w_q, model_w_q2, test="Chi")
Anova(model_w_q)
```

## * figure 
```{r}
Fig_Q_W <- 
  ggplot(q_estimate, aes(y = no_of_worker, x = total_queen_weight)) +
  stat_function(fun = function(x){exp(coef(model_w_q)[1] + coef(model_w_q)[2]*log(x))}) +
  geom_point(size = 3, shape = 1) +
  labs(y = "Number of workers in the colony",
       x = "Total weight of queens (mg)", 
       title ="") +
  scale_y_continuous(breaks=seq(0,450000,by=50000),limits=c(0,360000)) +
  scale_x_continuous(breaks=seq(0,6000,by=200),limits=c(0,1200)) +
  theme_classic()
Fig_Q_W

# save figure
ggsave(file = "Figure W Q.pdf", plot = Fig_Q_W, dpi = 300, width = 89, height = 89, units = c("mm"))
```

## * determinant coefficient (R^2)
```{r}
summary_ymean <- q_estimate %>% 
  summarize(mean = mean(no_of_worker))
mean <- summary_ymean$mean[1]

q_estimate_prep <- q_estimate %>% 
  mutate(pred = exp(coef(model_w_q)[1] + coef(model_w_q)[2]*log(total_queen_weight))) %>% 
  mutate(resid_square = (no_of_worker - pred)^2) %>% 
  mutate(deviation_square = (no_of_worker - mean)^2)

q_estimate_r2 <- q_estimate_prep %>% 
  summarize(numerator = sum(resid_square),
            denominator = sum(deviation_square)) %>% 
  mutate(r2 = 1 - numerator/denominator)

q_estimate_r2
```

# Colony size estimate in field colonies
```{r}
# data loading and estimation of number of workers in the colony
worker_estimate <- read_excel("Dataset.xlsx", sheet="colony size estimation") %>% 
  as.data.frame(.) %>% 
  mutate(daily_egg_production = round((exp(coef(model_eg)[1] + coef(model_eg)[2]*log(mean_body_weight_of_secondary_queen_mg)))*no_of_secondary_queen, 0)) %>% 
  mutate(W_estimate = round(exp(coef(model_w_egg)[1] + coef(model_w_egg)[2]*log(daily_egg_production)),0))
```

## * sample size
```{r}
summary_worker_estimate <- worker_estimate %>% 
  summarize(number = n(),
            first_quartile = quantile(W_estimate, 0.25, na.rm = TRUE), 
            median = median(W_estimate),
            third_quartile = quantile(W_estimate, 0.75, na.rm = TRUE), 
            max = max(W_estimate))
summary_worker_estimate
```

## * figure
```{r}
# colony size in the field
hist <-
ggplot(worker_estimate, aes(x = W_estimate)) +
  geom_histogram(boundary = 1, 
                 binwidth = 10000, 
                 color="black"
                 ) +
  scale_x_continuous(breaks = seq(0, 1000000, by = 50000), limits=c(0,480000), expand = c(0,0)) +  
  scale_y_continuous(breaks = seq(0, 100, by = 10), limits=c(0,48), expand = c(0,0)) + 
  labs(x = "Number of workers in the colony",
       y = "Number of colonies") +
  theme_classic()
hist
```
